A Spatial AR System for Wide-area Axis-aligned Metric Augmentation of Planar Scenes

### 2021-07-31 paper/elsarticle/elsarticle-template.tex
paper

\begin{keyword}
Spatial augmented reality (SAR) \sep computer vision \sep projector calibration \sep steerable mirror projection \sep Industry 4.0 \sep Pilotfabrik
\end{keyword}

@@

More generally, keystone correction for planar scenes can be said to reduce to computing a 2D homography \cite{Hartley2004}, an invertible transformation that preserves colinearity; this is the case whether computing the homography relies on manual interaction as in the case of Pinharez, or is obtained free of manual interaction as in ours. The intuition for why it is that a transformation that maps lines to lines can serve to model the appropriate image warp can be drawn from considering a planar chessboard pattern: looking at an image of a chessboard acquired from an oblique angle, one observes that lines parallel in the chessboard appear to meet in respective vanishing points; looking at an image of the same chessboard acquired frontally with respect to the plane of the chessboard, lines parallel in the chessboard appear parallel in the image (i.e., they are said to meet `at infinity'). To warp the former image (where lines parallel in the scene meet in respective vanishing points) such that the lines of the chessboard appear as in the latter image (where lines parallel in the scene meet at infinity), a transformation that maps lines to lines is sufficient.

@@

>>>>

\begin{keyword}
Spatial augmented reality (SAR) \sep computer vision \sep projector calibration \sep steerable mirror projector \sep Industry 4.0 \sep Pilotfabrik
\end{keyword}

@@

More generally, keystone correction for planar scenes can be said to reduce to computing a 2D homography \cite{Hartley2004}, an invertible transformation that preserves colinearity; this is the case whether computing the homography relies on manual interaction as in the case of Pinharez, or is obtained free of manual interaction as in ours. The intuition for why it is that a transformation that preserves colinearity---i.e., maps lines to lines---can serve to model an appropriate corrective image warp can be drawn from considering a planar chessboard pattern: looking at an image of a chessboard acquired from an oblique angle, one observes that lines parallel in the chessboard appear to meet in respective vanishing points; looking at an image of the same chessboard acquired frontally with respect to the plane of the chessboard, lines parallel in the chessboard appear parallel in the image (i.e., they are said to meet `at infinity'). To warp the former image (where lines parallel in the scene meet in respective vanishing points) such that the lines of the chessboard appear as in the latter image (where lines parallel in the scene meet at infinity), a transformation that maps lines to lines is sufficient.

@@

\begin{figure}
    \centering
    \subfloat[\centering Hardware setup (projector, steerable mirror system, camera).]{{\includegraphics[height=3.3cm]{images/system2.png}}}
    \quad
    \subfloat[\centering Example projection of image warped for target location using our approach.]{{\includegraphics[height=3.3cm]{images/hans_undist.png}}}
    \caption{Evaluation scenario. (a) Our hardware setup, comprised of a Panasonic PT-RZ660BE projector, a steerable mirror system manufactured by Dynamic Projection Institute, and a Stereolabs Zed 2 stereo camera, of which we used only the left view. (b) Example augmentation produced by projecting---to one of our 15 target locations---an image warped using our approach, as seen from the downwards-facing camera. Note that the warp places the axes of the augmentation in accordance with the axes of the camera, and that the dimensions of the augmentation are in line with the desired target dimensions (50~cm~$\times$~31.25~cm). Corners of the full projected image extent projected to the floor in light green.}
    \label{fig:eval}
\end{figure}
